Figures to insert in text

### 2018-04-03 kanerva-answer.tex
SDM Answer to Dr K.

Hence, let $Z$ be the number of activated hard location with the same bit as the reading address, then: $Z = \sum_{i=1}^{h} X_i$, where $\mathbf{E}[h] = h$, $\mathbf{V}[h] = H p_1 (1-p_1)$, $p_1 = 2^{-n} \sum_{k=0}^{r} \binom{n}{k}$, and $X_i \sim \text{Bernoulli}(p)$. By the central limit theorem, $Z$ is normally distributed with $\mathbf{E}[Z] = \mathbf{E}[\mathbf{E}[W_i | h]] = \mathbf{E}[ph] = p \mathbf{E}[h] = ph$, and $\mathbf{V}[Z] = \mathbf{E}[\mathbf{V}[X_i|h]] + \mathbf{V}[\mathbf{E}[X_i|h]] = \mathbf{E}[hp(1-p)] + \mathbf{V}[ph] = p(1-p) \mathbf{E}[h] + p^2 \mathbf{V}[h] = hp(1-p) + p^2 H p_1 (1-p_1)$. See Figure \ref{fig:sdm-same-bit-histogram} for a comparison between the theoretical model and a simulation.

@@

Let $\theta = \frac{sh}{H}$ be the average number of bitstrings written in each hard location, and $X_k \sim \text{Bernoulli}(p)$ (where $p = P(x_i = y_i | d(x, y) \le r)$). Thus, $Y_i = \sum_{k=1}^{\theta} X_k \sim \mathcal{N}(\mu_1, \sigma_1^2)$ with $\mu_1 = p \theta$, and $\sigma_1^2 = p(1-p) \theta + p^2 s^2 p_1 (1 - p_1) / H$.

@@

However, for ``x at x'', $p=0.5529$ and the probabilities depend on $s$. For $s=10,000$, they are equal to 0.6354. For $s=20,000$, they are equal to 0.6867. For $s=30,000$, they are equal to 0.7232. The more random bitstrings are written into the memory, the more a hard location to point to itself. See Figure \ref{fig:sdm-corr-prob} --- and notice that I still have to figure out why the mean is correct, but the standard deviation is not. As each of the $n$ counters of a hard location may be equal or not with the same probability, I assumed it would follow a Binomial distribution (and it worked for ``random at x'').

@@

Let $\eta$ be the reading address and $\eta_i$ the $i$th bit of it. Then,

\begin{align}
\left[ \text{acc}_i|\eta_i=1 \right] &= \sum_{k=1}^{ph} \left[ \text{cnt}_k | \text{addr}_k=1 \right] + \sum_{k=1}^{(1-p)h} \left[ \text{cnt}_k | \text{addr}_k=0 \right] \\
\left[ \text{acc}_i|\eta_i=0 \right] &= \sum_{k=1}^{ph} \left[ \text{cnt}_k | \text{addr}_k=0 \right] + \sum_{k=1}^{(1-p)h} \left[ \text{cnt}_k | \text{addr}_k=1 \right]
\end{align}

We may analyze only one case, because the probability of the other is exactly the same.

@@

\begin{align}
\sum_{k=1}^{ph} \left[ \text{cnt}_k | \text{addr}_k=1 \right] &\sim \mathcal{N}(\mu_3 = \mu_2 ph, \sigma_3^2 = \sigma_2^2 ph + \mu_2^2 h p(1-p)) \label{eqn:sdm-eta1-addr1} \\
\sum_{k=1}^{(1-p)h} \left[ \text{cnt}_k | \text{addr}_k=0 \right] &\sim \mathcal{N}(\mu_3 = -\mu_2 (1-p)h, \sigma_3^2 = \sigma_2^2 (1-p)h + \mu_2^2 h p (1-p)) \label{eqn:sdm-eta1-addr0}
\end{align}

>>>>

Hence, let $Z$ be the number of activated hard location with the same bit as the reading address, then: $Z = \sum_{i=1}^{h} X_i$, where $\mathbf{E}[h] = h$, $\mathbf{V}[h] = H p_1 (1-p_1)$, $p_1 = 2^{-n} \sum_{k=0}^{r} \binom{n}{k}$, and $X_i \sim \text{Bernoulli}(p)$. By the central limit theorem, $Z$ is normally distributed.

Applying the law of total average and the law of total variance, $\mathbf{E}[Z] = \mathbf{E}[\mathbf{E}[Z | h]] = \mathbf{E}[ph] = p \mathbf{E}[h] = ph$, and $\mathbf{V}[Z] = \mathbf{E}[\mathbf{V}[Z|h]] + \mathbf{V}[\mathbf{E}[Z|h]] = \mathbf{E}[hp(1-p)] + \mathbf{V}[ph] = p(1-p) \mathbf{E}[h] + p^2 \mathbf{V}[h] = hp(1-p) + p^2 H p_1 (1-p_1)$.

See Figure \ref{fig:sdm-same-bit-histogram} for a comparison between the theoretical model and a simulation.

@@

Let $\theta = \frac{sh}{H}$ be the average number of bitstrings written in each hard location, and $X_k \sim \text{Bernoulli}(p)$ (where $p = P(x_i = y_i | d(x, y) \le r)$). Thus,

\begin{align}
Y_i = \sum_{k=1}^{\theta} X_k \sim \mathcal{N}(\mu_1 = p \theta, \sigma_1^2 = p(1-p) \theta + p^2 s^2 p_1 (1 - p_1) / H)
\end{align}

@@

However, for ``x at x'', $p=0.5529$ and the probabilities depend on $s$. For $s=10,000$, they are equal to 0.6354. For $s=20,000$, they are equal to 0.6867. For $s=30,000$, they are equal to 0.7232. The more random bitstrings are written into the memory, the more the hard locations point to themselves. See Figure \ref{fig:sdm-corr-prob} --- and notice that I still have to figure out why the mean is correct, but the standard deviation is not. As each of the $n$ counters of a hard location may be equal or not with the same probability, I assumed it would follow a Binomial distribution (and it worked for ``random at x'').

@@

Let $\eta$ be the reading address and $\eta_i$ the $i$th bit of it. Then, let's split the $h$ activated hard locations into two groups: (i) the ones with the same bit as $\eta_i$ with $ph$ hard locations, and (ii) the ones with the opposite bit as $\eta_i$ with $(1-p)h$ hard locations.

\begin{align}
\left[ \text{acc}_i|\eta_i \right] &= \sum_{k=1}^{ph} \left[ \text{cnt}_k | \text{addr}_k=\eta_i \right] + \sum_{k=1}^{(1-p)h} \left[ \text{cnt}_k | \text{addr}_k \ne \eta_i \right]
\end{align}

@@

\begin{align}
\sum_{k=1}^{ph} \left[ \text{cnt}_k | \text{addr}_k=\eta_1 \right] &\sim \mathcal{N}(\mu_3 = \mu_2 ph, \sigma_3^2 = \sigma_2^2 ph + \mu_2^2 h p(1-p)) \label{eqn:sdm-eta1-addr1} \\
\sum_{k=1}^{(1-p)h} \left[ \text{cnt}_k | \text{addr}_k \ne \eta_1 \right] &\sim \mathcal{N}(\mu_3 = -\mu_2 (1-p)h, \sigma_3^2 = \sigma_2^2 (1-p)h + \mu_2^2 h p (1-p)) \label{eqn:sdm-eta1-addr0}
\end{align}
